rapr: Representative and Adequate Prioritisations in R

### 2016-06-23 code/rmarkdown/article.Rmd
+ fix incorrect ref in article

## CASE STUDY 2
### Methods
Here we used of space-based targets to generate a prioritisation to secure a representative sample of a species' intra-specific genetic variation. We used species occurrence and genomic data collected by the international IntraBioDiv project in the European Alps [@462; see @r461 and @r463 for further explanation of data collection methods]. Althougthis dataset contains multiple plant species, we used data for the `r  cs2.params.LST[[MODE]]$common.name` (\textit{`r gsub('_', ' ',cs2.params.LST[[MODE]]$species.name,fixed=TRUE)`}). This species was chosen because it provides is locally wide-spread and has been shown to exhibit significant genetic structure [@r454]. Members of the IntraBioDiv project collected data using a $20^{\prime}$ longitude by $21^{\prime}$ latitude grid (approx. 22.3 km $\times$ 25 km; Fig. 7a). They visited every second grid cell, and if the `r cs2.params.LST[[MODE]]$common.name` was detected in a cell, samples were collected from three individuals. Samples were genotyped using amplified fragment length polymorphisms [AFLP; @r453], and used to construct matrices denoting the presence/absence of polymorphisms at loci. In total, `r structurer::n.samples(cs2.spp.StructureData.LST[[1]])` individuals were genotyped at `r structurer::n.loci(cs2.spp.StructureData.LST[[1]])` markers.

>>>>

## CASE STUDY 2
### Methods
Here we used of space-based targets to generate a prioritisation to secure a representative sample of a species' intra-specific genetic variation. We used species occurrence and genomic data collected by the international IntraBioDiv project in the European Alps [@r462; see @r461 and @r463 for further explanation of data collection methods]. Althougthis dataset contains multiple plant species, we used data for the `r  cs2.params.LST[[MODE]]$common.name` (\textit{`r gsub('_', ' ',cs2.params.LST[[MODE]]$species.name,fixed=TRUE)`}). This species was chosen because it provides is locally wide-spread and has been shown to exhibit significant genetic structure [@r454]. Members of the IntraBioDiv project collected data using a $20^{\prime}$ longitude by $21^{\prime}$ latitude grid (approx. 22.3 km $\times$ 25 km; Fig. 7a). They visited every second grid cell, and if the `r cs2.params.LST[[MODE]]$common.name` was detected in a cell, samples were collected from three individuals. Samples were genotyped using amplified fragment length polymorphisms [AFLP; @r453], and used to construct matrices denoting the presence/absence of polymorphisms at loci. In total, `r structurer::n.samples(cs2.spp.StructureData.LST[[1]])` individuals were genotyped at `r structurer::n.loci(cs2.spp.StructureData.LST[[1]])` markers.
